---
title: "20210217 Project 1 Biologist"
author: "Allison Nau"
date: "2/24/2021"
output: html_document
---
This version of the script was used to produce the gene name mapping used in 
table 2 for the analyst.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Login to scc:
ssh -X anau@scc2.bu.edu

General project info:
/project/bf528/project_1/doc/

Change to project directory:
cd /project/bf528/project_1
cd data
cd /projectnb2/bf528/users/dachshund/project_1

Make directory
mkdir biologist

Long form listing with permissions:
ls -la

To install bioconductor:
if (!requireNamespace("BiocManager", quietly = TRUE))
  install.packages("BiocManager")
BiocManager::install(version = "3.12")

TO install packages
BiocManager::install(c("hgu133plus2.db"))
BiocManager::install(c("GSEABase"))

***



```{r}
# Load libraries
library("hgu133plus2.db")
library(GSEABase)
library(tidyverse)
library(dplyr)
library(knitr)
library(kableExtra)

# To check memory limit and adjust (on pc):
# memory.limit()  # To check
# memory.limit()
```
```{r}
# Package citation commands:
citation("hgu133plus2.db")
citation("GSEABase")
```


```{r}
# Read in differential expression results:
diff_exp <- read.csv(file="project_1_step_5_6_2_fromanalyst_20210222v3_mod.csv", header = TRUE)

diff_exp_top <- read.csv(file="top_mr.csv", header = TRUE)
diff_exp_bottom <- read.csv(file="bottom_mr.csv", header = TRUE)

```

```{r}
# Map probeset IDs
gene_symbol_matches <- AnnotationDbi::select(hgu133plus2.db, keys=diff_exp$probe, columns=("SYMBOL"))

gene_symbol_matches_top <- AnnotationDbi::select(hgu133plus2.db, keys=diff_exp_top$probe, columns=("SYMBOL"))
write.csv(gene_symbol_matches_top, file="forMRtop.csv")
gene_symbol_matches_bottom <- AnnotationDbi::select(hgu133plus2.db, keys=diff_exp_bottom$probe, columns=("SYMBOL"))
write.csv(gene_symbol_matches_bottom, file="forMRbottom.csv")

```
